---
title: "CS LGBT Network - data review"
output: 
  flexdashboard::flex_dashboard
---

```{r setup LGB+ & heterosexual sheet, include=FALSE}

#load packages
library(flexdashboard)
library(tidyverse)
library(dplyr)
library(readxl)
library(stringr)
library(janitor)
library(naniar)
library(plotly)

#Read in 2020 People survey data for LGB+
LGB2020 <- read_excel("C:/Users/prile/OneDrive/cs-lgbt/cs-lgbt-dashboard/Data/LGB_2020.xlsx",
           sheet = "LGB+", col_names = TRUE)

#Remove top 3 rows as they don't include relevant data
LGB2020 <- LGB2020[-c(1:3), ]

#Make first row the new headers, and change some column names to something small
LGB2020 <- row_to_names(LGB2020, 1)

LGB2020 <- rename(LGB2020, "Demo_info" = "Demographic variable [1, 5, 6]",
                  "ees" = colnames(LGB2020)[4],
                  "mw_p" = colnames(LGB2020)[5],
                  "op_p" = colnames(LGB2020)[6],
                  "lm_p" = colnames(LGB2020)[7],
                  "mt_p" = colnames(LGB2020)[8],
                  "ld_p" = colnames(LGB2020)[9],
                  "if_p" = colnames(LGB2020)[10],
                  "rw_p" = colnames(LGB2020)[11],
                  "pb_p" = colnames(LGB2020)[12],
                  "lc_p" = colnames(LGB2020)[13],
                  "B03" = colnames(LGB2020)[18],
                  "E01" = colnames(LGB2020)[83],
                  "E03" = colnames(LGB2020)[104]
)

#Transform data into tidy format for easier analysis
LGBTidy <- LGB2020 %>% 
            gather(Question, percentage, -Demo_info, -Response, -Count) %>% 
  mutate(Demo_info_three = gsub(":.*","", Demo_info))

#Merge Annexes with the demo_info and questions so that the info is available
#Start by reading in annex tabs into dfs
demoQuestions <- read_excel("C:/Users/prile/OneDrive/cs-lgbt/cs-lgbt-dashboard/Data/LGB_2020.xlsx",
                            sheet = "Annex_1", col_names = FALSE)

surveyQuestions <- read_excel("C:/Users/prile/OneDrive/cs-lgbt/cs-lgbt-dashboard/Data/LGB_2020.xlsx",
                              sheet = "Annex_2", col_names = FALSE)


#Make the fourth row the new column names for demographic annex questions
demoQuestions <- row_to_names(demoQuestions, 4)
demoQuestions <- rename(demoQuestions, "Question_code" = "Question code [1, 5, 6]",
                                       "Question_label" = "Question label")

#Make fourth row the new column name for the survey questions
surveyQuestions <- row_to_names(surveyQuestions, 4)
surveyQuestions <- rename(surveyQuestions, "Question_code" = "Question code [2, 3, 4]",
                                           "Question_label" = "Question label [7]")


#Merge annexes with the question codes in master df
LGBTidyMerge <- left_join(LGBTidy, demoQuestions, by = c("Demo_info_three" = "Question_code"))

LGBTidyMerge <- left_join(LGBTidyMerge, surveyQuestions, by = c("Question" = "Question_code"))


#Tidy up columns by removing question codes and renaming duplicated cols
LGBTidyNewCols <- LGBTidyMerge %>% 
                    select(-Demo_info, -Question) %>% 
                    rename("Demo_question" = "Question_label.x",
                           "Survey_question" = "Question_label.y",
                           "Demo_response" = "Response")


#Reorder columns in a more useful way
#LGBOrdered <- LGBTidyNewCols[, c(4, 1, 2, 5, 3)]

#Summarise data to check data types
#summary(LGBOrdered)

#Make columns into correct data types
#change data types
LGBDataTypes <- LGBTidyNewCols %>%
                transform(Count = as.numeric(Count),
                          percentage = as.numeric(percentage),
                          Demo_question = as.factor(Demo_question),
                          Survey_question = as.factor(Survey_question))

#Check structure and summarise data after changes
#[c] stands for suppressed in the data, which has been changed to NA during data type change
str(LGBDataTypes)
summary(LGBDataTypes)


################################ Heterosexual sheet #################################################################
#Read in 2020 People survey data for heterosexual
heterosexual2020 <- read_excel("C:/Users/prile/OneDrive/cs-lgbt/cs-lgbt-dashboard/Data/LGB_2020.xlsx",
           sheet = "Heterosexual", col_names = TRUE)

#Remove top 3 rows as they don't include relevant data
heterosexual2020 <- heterosexual2020[-c(1:3), ]

#Make first row the new headers, and change some column names to something small
heterosexual2020 <- row_to_names(heterosexual2020, 1)

heterosexual2020 <- rename(heterosexual2020, "Demo_info" = "Demographic variable [1, 5, 6]",
                  "ees" = colnames(heterosexual2020)[4],
                  "mw_p" = colnames(heterosexual2020)[5],
                  "op_p" = colnames(heterosexual2020)[6],
                  "lm_p" = colnames(heterosexual2020)[7],
                  "mt_p" = colnames(heterosexual2020)[8],
                  "ld_p" = colnames(heterosexual2020)[9],
                  "if_p" = colnames(heterosexual2020)[10],
                  "rw_p" = colnames(heterosexual2020)[11],
                  "pb_p" = colnames(heterosexual2020)[12],
                  "lc_p" = colnames(heterosexual2020)[13],
                  "B03" = colnames(heterosexual2020)[18],
                  "E01" = colnames(heterosexual2020)[83],
                  "E03" = colnames(heterosexual2020)[104]
)

#Transform data into tidy format for easier analysis
heterosexualTidy <- heterosexual2020 %>% 
            gather(Question, percentage, -Demo_info, -Response, -Count) %>% 
  mutate(Demo_info_three = gsub(":.*","", Demo_info))

#Merge Annexes with the demo_info and questions so that the info is available




#Merge annexes with the question codes in master df
heterosexualTidyMerge <- left_join(heterosexualTidy, demoQuestions, by = c("Demo_info_three" = "Question_code"))

heterosexualTidyMerge <- left_join(heterosexualTidyMerge, surveyQuestions, by = c("Question" = "Question_code"))


#Tidy up columns by removing question codes and renaming duplicated cols
heterosexualidyNewCols <- heterosexualTidyMerge %>% 
                    select(-Demo_info, -Question) %>% 
                    rename("Demo_question" = "Question_label.x",
                           "Survey_question" = "Question_label.y",
                           "Demo_response" = "Response")


#Make columns into correct data types
#change data types
heterosexualDataTypes <- heterosexualidyNewCols %>%
                transform(Count = as.numeric(Count),
                          percentage = as.numeric(percentage),
                          Demo_question = as.factor(Demo_question),
                          Survey_question = as.factor(Survey_question))

#Check structure and summarise data after changes
#[c] stands for suppressed in the data, which has been changed to NA during data type change
str(heterosexualDataTypes)
summary(heterosexualDataTypes)






```


```{r bullying, include = FALSE}




## Ethnicity -----------------------------------------------------------------------------------------------


#Summarise data to analyse
#Look at ethnicity info and question of bullying
LGBEthnicityBullying <- LGBDataTypes %>% 
                      filter(Demo_question == "Ethnicities (full)", 
                             Survey_question == "Have you been bullied or harassed at work, in the past 12 months? (% yes)") %>% 
  mutate(sexuality = "LGB+")


heterosexualEthnicityBullying <- heterosexualDataTypes %>% 
                      filter(Demo_question == "Ethnicities (full)", 
                             Survey_question == "Have you been bullied or harassed at work, in the past 12 months? (% yes)") %>% 
  mutate(sexuality = "Heterosexual")


EthnicityBullying <- LGBEthnicityBullying %>% 
  bind_rows(heterosexualEthnicityBullying)


## Sexual orientation ----------------------------------------------------------------------------------------------------------

#Look at bullying and harassment info for LGB
LGBsexualOrientationBullying <- LGBDataTypes %>% 
                      filter(Demo_question == "Which of the following (sexual orientation) options best describes how you think of yourself?", 
                              Survey_question == "Have you been bullied or harassed at work, in the past 12 months? (% yes)") %>% 
  mutate(sexuality = "LGB+")


heterosexualsexualOrientationBullying <- heterosexualDataTypes %>% 
                      filter(Demo_question == "Which of the following (sexual orientation) options best describes how you think of yourself?", 
                              Survey_question == "Have you been bullied or harassed at work, in the past 12 months? (% yes)") %>% 
  mutate(sexuality = "Heterosexual")

sexualOrientationBullying <- LGBsexualOrientationBullying %>% 
  bind_rows(heterosexualsexualOrientationBullying)

## By organisation -------------------------------------------------------------------------------------------------------
#Look at organisations and their score for bullying
orgBullying <- read_excel("C:/Users/prile/OneDrive/cs-lgbt/cs-lgbt-dashboard/Data/LGB_2020.xlsx",
                              sheet = "Organisations", col_names = FALSE)

#Remove unnecessary rows and make column names 
orgBullying <- row_to_names(orgBullying, 5) 

#Replace suppressed values with NA
orgBullying[orgBullying == '[c]'] <- NA


#Reduce dataframe to important columns
orgBullyingShort <- orgBullying %>% 
                      select('Organisation group', 'Organisation name', 'Response [1]', 'Count', "E03: Have you been bullied or harassed at work, in the past 12 months? (% yes) [4]" )


#Rename columns to easier ones
orgBullyingShort <- rename(orgBullyingShort, "OrgGroup" = "Organisation group",
                                             "OrgName" = "Organisation name",
                                             "Response" = "Response [1]",
                                             "Bullying" = "E03: Have you been bullied or harassed at work, in the past 12 months? (% yes) [4]" )

#group by organisation group and filter by LGB+ responses only
#Transform the columns that need to be numeric and also remove NAs
LGBOrgBullying <- orgBullyingShort %>%
                      transform(Count = as.numeric(Count),
                                Bullying = as.numeric(Bullying)) %>% 
                      na.omit() %>% 
                      filter(Response == "LGB+")

heterosexualOrgBullying <- orgBullyingShort %>%
                      transform(Count = as.numeric(Count),
                                Bullying = as.numeric(Bullying)) %>% 
                      na.omit() %>% 
                      filter(Response == "Heterosexual/straight")

#Group by Organisation group and create column with median score
LGBOrgBullyingGroup <- LGBOrgBullying %>% 
                          group_by(OrgGroup) %>%
                          summarise_at(vars(Bullying), list(Average = median)) %>% 
  mutate(sexuality = "LGB+")

heterosexualOrgBullyingGroup <- heterosexualOrgBullying %>% 
                                  group_by(OrgGroup) %>%
                                  summarise_at(vars(Bullying), list(Average = median)) %>% 
  mutate(sexuality = "Heterosexual")


OrgBullyingGroup <- LGBOrgBullyingGroup %>% 
  bind_rows(heterosexualOrgBullyingGroup)


# SEB status (self-declared) ---------------------------------------------------------------------------------------------------------------------------------------------------

LGBSEBBullying <- LGBDataTypes %>% 
                      filter(Demo_question == "Compared to people in general, would you describe yourself as coming from a lower socio-economic background?", 
                              Survey_question == "Have you been bullied or harassed at work, in the past 12 months? (% yes)") %>% 
  mutate(sexuality = "LGB+")


heterosexualSEBBullying <- heterosexualDataTypes %>% 
                      filter(Demo_question == "Compared to people in general, would you describe yourself as coming from a lower socio-economic background?", 
                              Survey_question == "Have you been bullied or harassed at work, in the past 12 months? (% yes)") %>% 
  mutate(sexuality = "Heterosexual")


SEBBullying <- LGBSEBBullying %>% 
  bind_rows(heterosexualSEBBullying)



# Location  ---------------------------------------------------------------------------------------------------------------------------------------------------

LGBLocationBullying <- LGBDataTypes %>% 
                      filter(Demo_question == "Where in England do you currently work?", 
                              Survey_question == "Have you been bullied or harassed at work, in the past 12 months? (% yes)") %>% 
  mutate(sexuality = "LGB+")


heterosexualLocationBullying <- heterosexualDataTypes %>% 
                      filter(Demo_question == "Where in England do you currently work?", 
                              Survey_question == "Have you been bullied or harassed at work, in the past 12 months? (% yes)") %>% 
  mutate(sexuality = "Heterosexual")


LocationBullying <- LGBLocationBullying %>% 
  bind_rows(heterosexualLocationBullying)


```


```{r Career development}

# Accomplishment question

LGBsexualorientationAcc <- LGBDataTypes %>% 
                      filter(Demo_question == "Which of the following (sexual orientation) options best describes how you think of yourself?", 
                              Survey_question == "My work gives me a sense of personal accomplishment (% strongly agree or agree)") %>% 
  mutate(sexuality = "LGB+")


heterosexualsexualorientationAcc <- heterosexualDataTypes %>% 
                      filter(Demo_question == "Which of the following (sexual orientation) options best describes how you think of yourself?", 
                              Survey_question == "My work gives me a sense of personal accomplishment (% strongly agree or agree)") %>% 
  mutate(sexuality = "Heterosexual")


sexualorientationAcc <- LGBsexualorientationAcc %>% 
  bind_rows(heterosexualsexualorientationAcc)



# Employee engagement index index

# Accomplishment question

LGBsexualorientationEEI <- LGBDataTypes %>% 
                      filter(Demo_question == "Which of the following (sexual orientation) options best describes how you think of yourself?", 
                              Survey_question == "Employee engagement index (B47 to B51)") %>% 
  mutate(sexuality = "LGB+")


heterosexualsexualorientationEEI <- heterosexualDataTypes %>% 
                      filter(Demo_question == "Which of the following (sexual orientation) options best describes how you think of yourself?", 
                              Survey_question == "Employee engagement index (B47 to B51)") %>% 
  mutate(sexuality = "Heterosexual")


sexualorientationEEI <- LGBsexualorientationEEI %>% 
  bind_rows(heterosexualsexualorientationEEI)

```

About this tool
===============================================

This is a prototype tool contains a "storyboard"-type dashboard. It contains analysis on the 2020 Civil Service People Survey dataset for LGB+ respondents and heterosexual respondents on some key areas.

This work is not an output under national, official or experimental statistics. It does use [publicly available data from the Civil Service People Survey, published by the Cabinet Office](https://www.gov.uk/government/publications/civil-service-people-survey-2021-results).

Any blank data indicates data supression under dominance & disclosure rules.

*It is possible to zoom in & out of these graphs.*

This work has been on a voluntary basis with colleagues who are part of the [Civil Service LGBT+ Network](www.civilservice.lgbt) data team. They are civil servants.
* T Elliot
* P Riley
* J Smith
* J Peart (network coordinator)


Bullying {.storyboard}
===============================================


### By ethnicity

```{r}
p1 <- ggplot(EthnicityBullying, aes(x = Demo_response, y = percentage, fill = sexuality)) +
  geom_bar(stat = "identity", position = position_dodge())+
  labs(x = "", y = "% bullied (heterosexual)",
       title = "Heterosexual colleagues experiencing bullying, by ethnicity") +
  theme(axis.text.x = element_text(colour = "black", size = 8, angle = 45, vjust = .8, hjust = 0.8)) +
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, 15)) +
  coord_flip()

ggplotly(p1)

```



### By sexual orientation

```{r}
p2 <- ggplot(sexualOrientationBullying, aes(x = Demo_response, y = percentage)) +
  geom_bar(stat = "identity") +
  labs(x = "", y = "% bullied",
       title = "Percentage of colleagues experiencing bullying, by sexual orientation") +
  theme(axis.text.x = element_text(colour = "black", size = 8, angle = 90, vjust = .8, hjust = 0.8)) + 
  coord_flip()


ggplotly(p2)

```

### SEB indicator


```{r}
p3 <- ggplot(SEBBullying, aes(x = Demo_response, y = percentage, fill = sexuality)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(x = "", y = "% bullied",
       title = "Percentage of colleagues experiencing bullying, by sexual orientation") +
  theme(axis.text.x = element_text(colour = "black", size = 8, angle = 90, vjust = .8, hjust = 0.8)) + 
  coord_flip()


ggplotly(p3)

```

### Sexual orientation, by department

```{r}
p4 <- ggplot(OrgBullyingGroup, aes(x = OrgGroup, y = Average, fill = sexuality)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(x = "", y = "Average % of LGB+ colleagues bullied",
       title = "Median percentage of LGB+ colleagues experiencing bullying per Civil Service Organisation (group level)")+
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, 40)) +
  scale_y_continuous(breaks = seq(0, 30, 10)) +
  theme(axis.text.x = element_text(colour = "black", size = 8, angle = 90, vjust = .8, hjust = 0.8)) + 
  coord_flip()


ggplotly(p4)

```




### Location

```{r}
p5 <- ggplot(LocationBullying, aes(x = Demo_response, y = percentage, fill = sexuality)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(x = "", y = "% bullied",
       title = "Percentage of colleagues experiencing bullying, by location") +
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, 20)) +
  theme(axis.text.x = element_text(colour = "black", size = 8, angle = 90, vjust = .8, hjust = 0.8)) + 
  coord_flip()


ggplotly(p5)

```



Career progression, L&D {.storyboard}
===============================================


### Sense of accomplishment 

```{r}
p6 <- ggplot(sexualorientationAcc, aes(x = Demo_response, y = percentage)) +
  geom_bar(stat = "identity",) +
  labs(x = "", y = "% score",
       title = "Percentage of colleagues with a sense of accomplishment, by sexual orientation") +
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, 20)) +
  theme(axis.text.x = element_text(colour = "black", size = 8, angle = 90, vjust = .8, hjust = 0.8)) + 
  coord_flip()


ggplotly(p6)

```

### Employee Engagement Index (this is an index, not individual question)

```{r}
p7 <- ggplot(sexualorientationEEI, aes(x = Demo_response, y = percentage)) +
  geom_bar(stat = "identity",) +
  labs(x = "", y = "% score",
       title = "Employee engagement index, by sexual orientation") +
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, 20)) +
  theme(axis.text.x = element_text(colour = "black", size = 8, angle = 90, vjust = .8, hjust = 0.8)) + 
  coord_flip()


ggplotly(p7)


```


